\LARGE\textbf{Designing Studies and Evaluating Research Results:\\ Type M and Type S Errors for Pearson Correlation Coefficient }

### 2020-05-04 Documents/Paper_main/Paper_main.Rnw
Corrige table 2

data_table2 %>%
  filter(duplicated(sig_level)) %>%
  mutate_at(vars(typeM:crit_r), round, 3) %>%
  mutate(power=round(power,3),
         crit_r = paste0("$\\pm",crit_r,"$")) %>%
  dplyr::select(sig_level, power, typeM, typeS, crit_r) %>%
  kable(.,"latex", booktabs=T,align = "c",col.names = c("$\\bm{\\alpha}$-level", "Power", "Type M", "Type S", "Critical \\textit{r} value"),caption = "How changes in $\\alpha$ level impact Power, Type M error, Type S error and critical values.", escape = FALSE) %>%
  row_spec(0,bold = T, align = "c") %>%
  kable_styling(position = "center", latex_options = "HOLD_position")%>%
  footnote(general = 'In all cases, $\\rho=.25$, n = 13, and alternative  = \\\\texttt{"two.sided"}.',footnote_as_chunk = T,escape=F)

>>>>

data_table2 %>%
  filter(duplicated(sig_level)) %>%
  mutate_at(vars(typeM:crit_r), round, 3) %>%
  mutate(power=round(power,3),
         crit_r = paste0("$\\pm",crit_r,"$")) %>%
  dplyr::select(sig_level, power, typeM, typeS, crit_r) %>%
  kable(.,"latex", booktabs=T,align = "c",col.names = c("$\\bm{\\alpha}$-level", "Power", "Type M", "Type S", "Critical \\textit{r} value"),caption = "How changes in $\\alpha$ level impact Power, Type M error, Type S error and critical values.", escape = FALSE) %>%
  row_spec(0,bold = T, align = "c") %>%
  kable_styling(position = "center", latex_options = "HOLD_position")%>%
  footnote(general = 'In all cases, $\\\\rho=.25$, n = 13, and alternative  = \\\\texttt{"two.sided"}.',footnote_as_chunk = T,escape=F)
